Computing Entropies With Nested Sampling

### 2017-07-06 paper/ms.tex
Added paragraph and reference to Szabo

>>>>

Entropies, and related quantities, tend to be analytically available only for
a few families of probability distributions. On the numerical side, if
$\log p(x)$ can be evaluated for any $x$, then simple Monte Carlo will suffice
for approximating $H(x)$. On the other hand, if $p(x)$ can only be
{\em sampled} but not evaluated (for example, if $p(x)$ is a marginal
distribution), then this will not work. Kernel density estimation or the like
\citep[e.g.][]{JMLR:v15:szabo14a}
may be effective in this case, but is unlikely to generalise well to high
dimensions.

This paper introduces a computational approach to evaluating the entropy 
$H(x)$ of probability distributions that can only be sampled
(using Markov Chain Monte Carlo).
